Coldplay vs Radiohead Danceability over Time

### 2024-10-10 paper/paper.qmd
Update paper.qmd

---
title: "Coldplay vs Radiohead Danceability over Time"
subtitle: "Coldplay reamins more danceable over the years"
author: 
  - Chenika Bukes
  - Khushaal Nandwani
  - Yongkyung Ko
thanks: "Code and data are available at: https://github.com/chenikabukes/RadioheadColdplay"
date: today
date-format: long
abstract: "This study explores the danceability of Coldplay and Radiohead over time by using data extracted from Spotify’s API. The results show that Coldplay has consistently maintained a higher level of danceability compared to Radiohead. These findings are relevant in understanding the musical evolution of both bands and their appeal to different types of listeners."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Coldplay vs Radiohead Danceability over Time"
subtitle: "Coldplay reamins more danceable over the years"
author: 
  - Chenika Bukes
  - Khushaal Nandwani
  - Yunkyung Ko
thanks: "Code and data are available at: https://github.com/chenikabukes/RadioheadColdplay"
date: today
date-format: long
abstract: "This study explores the danceability of Coldplay and Radiohead over time by using data extracted from Spotify’s API. The results show that Coldplay has consistently maintained a higher level of danceability compared to Radiohead. These findings are relevant in understanding the musical evolution of both bands and their appeal to different types of listeners."
format: pdf
number-sections: true
bibliography: references.bib
---
